---
title: "Day 2 Interactive Session 2"
author: "Paloma Cartwright"
date: "03/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

### Plot a Function in `ggplot2`

```{r}

eq <- function(x){
  
  3 * x ^ 2 + 4
  
}

# Use stat_function() to plot it over a specific range: 

ggplot(data.frame(x = c(0, 100)), aes(x = x)) + 
  stat_function(fun = eq)



```

#### Assigned Task 

Plot $f(x) = 2.4 - 5x^3 + 2.1x^2$ over a range from -50 to 50 

```{r}

eqn <- function(x){
  2.4 - 5 * x ^ 3 + 2.1 * x ^ 2
}

ggplot(data.frame(x = c(-50, 50)), aes(x = x)) + 
  stat_function(fun = eqn)

# Another option is to use the following lines. This may be a little off but this is the idea, setting the data frame to NULL.
# ggplot(data.frame(NULL)) +
#   stat_function(fun = eqn) +
#   x_lim(min = 1, max = 100)
```

### Plot from the Penguins Data 

##### Completing this using `penguins` body mass and flipper lengths 

Make a basic `ggplot2` scatter plot of body mass (y) and flipper length (x)
```{r} 

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(aes(color = species)) +
  scale_color_manual(values = c("red", "purple", "green"))+ 
  labs(x = "Flipper Lengths (mm)", 
       y = "Body Mass (g)", 
       title = "Positive Correlation of Palmer Penguin Sizes", 
       subtitle = "Data collected by KB Gornat et al. at Palmer Station", 
       color = "Species"
       ) +
  # facet_wrap(~island) + (this made it look gross so I commented it out)
  theme_minimal()

```

The warning message above the `ggplot` is just to let me know that there are two penguins somewhere in the data that have something missing, either of the data points. 

### Higher Order Derivatives 

```{r}
gt <- expression( 2.2 + 3.1 * t - 5.6 * t ^ 4)

dg_dt <- D(expr = gt, "t")

dg_dt
```

```{r}
d2g_dt2 <- D(expr = dg_dt, "t")

d2g_dt2
```

### Partial Derivatives 

```{r}

f_xyz <- expression(2 * x * y - 3 * (x ^ 2) * (z^3) )

df_dx <- D(expr = f_xyz, "x")
df_dx

df_dy <- D(expr = f_xyz, "y")
df_dy

df_dz <- D(expr = f_xyz, "z")
df_dz
```

